Predicting Diamond Pricing: A Generalized Linear Model Analysis

### 2024-12-08 paper/paper.qmd
Update bibliography

---
title: "Predicting Diamond Pricing: A Generalized Linear Model Analysis"
subtitle: "Carat Weight Dominates While Cut Plays a Smaller Role in Determining Price"
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: "This paper investigates how the Four Cs—carat weight, color, clarity, and cut—affect diamond pricing and develops a predictive model using a Generalized Linear Model (GLM) with a Gamma distribution. The analysis shows that carat weight has the strongest positive influence on price, followed by clarity and color, while cut has a relatively smaller impact. The model demonstrates robust performance, providing a reliable framework for forecasting diamond prices and understanding market patterns. These findings enhance pricing transparency, help the diamond industry adapt to shifting consumer preferences, and provide opinions into the economic and cultural factors shaping diamond valuation."
format: pdf
number-sections: true
bibliography: 
  - references .bib
toc: true
---

>>>>

---
title: "Predicting Diamond Pricing: A Generalized Linear Model Analysis"
subtitle: "Carat Weight Dominates While Cut Plays a Smaller Role in Determining Price"
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: "This paper investigates how the Four Cs—carat weight, color, clarity, and cut—affect diamond pricing and develops a predictive model using a Generalized Linear Model (GLM) with a Gamma distribution. The analysis shows that carat weight has the strongest positive influence on price, followed by clarity and color, while cut has a relatively smaller impact. The model demonstrates robust performance, providing a reliable framework for forecasting diamond prices and understanding market patterns. These findings enhance pricing transparency, help the diamond industry adapt to shifting consumer preferences, and provide opinions into the economic and cultural factors shaping diamond valuation."
format: pdf
number-sections: true
bibliography: 
  - references.bib
toc: true
---
